Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-09 paper/v1.0/sections/2_schrodinger_problem.tex
Corrections appendix A

Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$. Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}. Thus, our system can be represented with a time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{\text{T}}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs. \cite{husimi53,ditt98,dini16}. Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_n t
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    &+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$. Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant. The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\omega_0 = eB/m_e$ being the cyclotron frequency and $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial.
The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
For details of the full derivation refer to Appendix \ref{appendix_a}.
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system. Therefore, we can observe that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

>>>>

Using Landau gauge for the stationary magnetic field, we can represent it as a vector potential $\vb{A}_{s} = (-By,0,0)^{\text{T}}$. Furthermore, we model the dynamic dressing field in the Coulomb gauge as $\vb{A}_{d}(t) = (0,[E/\omega ]\cos(\omega t),0)^{\text{T}}$. These vector potentials are coupled to the momentum of 2DEG as kinetic momentum \cite{mahan00,bruus04}. Thus, our system can be represented with a time-dependent Hamiltonian
\begin{equation} \label{eq_1}
  \hat{H}_e(t) = \frac{1}{2m_e}\Big[\hat{\vb{p}} - e\big[\vb{A}_{s}+\vb{A}_{d}(t)\big]\Big]^2,
\end{equation}
where $m_e$ is the effective electron mass, $e$ is the magnitude of the electron charge, and $\hat{\vb{p}} = (\hat{p}_x,\hat{p}_y,0)^{\text{T}}$ represents the canonical momentum operator for 2DEG with electron momentum $(p_{x},p_{y},0)^{\text{T}}$.
The exact solutions for the time-dependent Schrödinger equation $i\hbar\; \text{d}\psi/\text{d}t = \hat{H}_e(t) \psi$ were already derived in Refs. \cite{husimi53,ditt98,dini16}. Here we present them as a set of wave functions defined by two quantum numbers $(n,m)$
\begin{equation} \label{eq_2}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  \\
    & = \frac{1}{\sqrt{L_x}}
    \chi_n\big(y - y_0 - \zeta(t)\big)\\
    & \times
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_n t
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)\\
    &+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big] +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg),
  \end{aligned}
\end{equation}
where $n \in \mathbb{Z}^{+}_0$ and $m \in \mathbb{Z}$. Here $L_{x}$ and $L_{y}$ are dimensions of the 2DEG surface, and $\hbar$ is the reduced Planck constant. The center of the cyclotron orbit on the $y$-axis is given by $y_0 = -p_x/eB$ with $p_x = 2\pi \hbar m/L_x$.
Moreover, $\chi_n$ are well known eigenstate solutions for the Schrödinger equation of the stationary quantum harmonic oscillator
\begin{equation} \label{eq_3}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues $\epsilon_n = \hbar \omega_0 (n + 1/2)$ where $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, $\mathcal{H}_n(\cdot)$ is the $n$-th Hermite polynomial, and the cyclotron frequency $\omega_0 = eB/m_e$.
The path shift of the driven classical oscillator $\zeta(t)$ is given by
\begin{equation} \label{eq_4}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t),
\end{equation}
while the Lagrangian of the driven classical oscillator $L(\zeta,\dot{\zeta},t)$ can be identified as
\begin{equation} \label{eq_5}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2(t) - \frac{1}{2}m_e\omega_0^2 \zeta^2(t) + eE\zeta(t) \sin(\omega t).
\end{equation}
For details of the full derivation refer to Appendix \ref{appendix_a}.
The exponential phase shifts in Eq.~(\ref{eq_2}) represent the influence of the stationary magnetic field and dressing field on the electron behavior of our system. Therefore, we can observe that the magneto-transport characteristics of 2DEG can be renormalized by a nonoscillating magnetic field along with a dressing field.

### 2021-08-09 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections appendix A

As illustrated in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
For a given dressing field intensity, the longitudinal conductivity vary with  the Fermi level of the system showing sharp peaks at each Landau energy level.
In quantum Hall systems, electrons are restricted to bear only the Landau energies. Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels. In contrast, near each Landau level, the conductivity achieve excessive values compared to other areas. Moreover, as illustrates in Fig.~\ref{fig_5} the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.

>>>>

As illustrated in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considered system.
For a given dressing field intensity, the longitudinal conductivity vary with  the Fermi level of the system showing sharp peaks at each Landau energy level.
In quantum Hall systems, electrons are restricted to bear only the Landau energies. Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels. In contrast, near each Landau level, the conductivity achieve excessive values compared to other areas. Moreover, as illustrates in Fig.~\ref{fig_5} the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.

### 2021-08-09 paper/v1.0/sections/appendix_a.tex
Corrections for abstract and introduction
Corrections appendix A

The deriving process of solutions for time dependent Schrödinger equation with the Hamiltonian of our system (Eq. \ref{eq_1}) quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimentional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right],
\end{equation}
and since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both operators share same (simultaneous) eigenfunctions
$\frac{1}{\sqrt{L_x}}\exp(\frac{ip_x x}{\hbar})$ with $p_x = 2\pi \hbar m/L_x~,~ m \in \mathbb{Z}$.
Therefore, we re-arrange the Hamiltonian using definition of canonical momentum in $y$-direction to derive
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
We now define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 \equiv {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 \equiv {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Now we assume that the wave function solutions for the time-dependent Schrödinger equation of considering quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can present by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the following property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the strong dressing field ($E=0$), this equation leads to simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
It is important to notice that we can identify the $S(t) \equiv eE\sin(\omega t)$ part as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system can be exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53} as follows. We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t),
\end{equation}
and this yields
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Then we can restrict our $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that leads to
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify with the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y) \quad \text{with}
  \quad
  \kappa = \sqrt{\frac{m_e \omega_0}{\hbar}},
\end{equation}
which are propositional to the Hermite polynomials $\mathcal{H}_n$, with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~,~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Therefore, we can identify the solutions of Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since set $\{\chi_n(x)\}$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of solutions derived in Eq.~(\ref{eq_a18}).

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we can derive the solution for Eq.~(\ref{eq_a11}):
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we can obtain the set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_nt \\
    &
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
    & +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}

>>>>

The derivation of the solutions for the time dependent Schrödinger equation with our system's Hamiltonian (Eq. \ref{eq_1}) is quite similar to that followed in Refs. \cite{husimi53,dini16}. We start with expanding the Hamiltonian for two-dimensional case
\begin{equation} \label{eq_a1}
  \hat{H}_e(t) = \frac{1}{2m_e}\left[
    \left[\hat{p}_x + eBy \right]^2 +
    \left[\hat{p}_y - \frac{eE}{\omega}\cos(\omega t)\right]^2
  \right].
\end{equation}
Since $\left[\hat{H}_e(t),\hat{p}_x \right] =0$, both of these operators share same eigenfunctions
${L_x}^{-1/2}\exp(\frac{ip_x x}{\hbar})$ where $p_x = 2\pi \hbar m/L_x~$ with $ m \in \mathbb{Z}$.
Thus, we re-arrange the Hamiltonian using the definition of canonical momentum in $y$-direction and this leads to
\begin{equation} \label{eq_a2}
    \hat{H}_e(t) = \frac{1}{2m_e}\left[
      \left[{p}_x + eBy \right]^2 +
      \left[-i\hbar \pdv{y}- \frac{eE}{\omega}\cos(\omega t)\right]^2
    \right].
\end{equation}
Subsequenty we define the \textit{center of the cyclotron orbit} on the $y$-axis $y_0 = {-p_x}/{eB}$ and the \textit{cyclotron frequency} $\omega_0 = {eB}/{m_e}$. This leads to a new arrangement of the Hamiltonian
\begin{equation} \label{eq_a3}
  \begin{aligned}
    \hat{H}_e(t) =
      \frac{m_e \omega_0^2}{2}\tilde{y}^2 +
      \frac{1}{2m_e}\bigg[
      -\hbar^2 \pdv[2]{\tilde{y}} & +
      \frac{2i\hbar eE}{\omega}\cos(\omega t) \pdv{\tilde{y}} \\
      & +
      \frac{e^2E^2}{\omega^2}\cos[2](\omega t)
      \bigg],
  \end{aligned}
\end{equation}
where we used a variable substitution $\tilde{y} = (y - y_0)$. Furthermore, we assume that the wave function solutions for the time-dependent Schrödinger equation of considered quantum system
\begin{equation} \label{eq_a4}
    i \hbar \dv{\psi}{t} = \hat{H}_e(t)\psi,
\end{equation}
can be presented by the following form
\begin{equation} \label{eq_a5}
    \psi_m(x,\tilde{y},t) = \frac{1}{\sqrt{L_x}} \exp\bigg(
      \frac{ip_x x}{\hbar} +
      \frac{ieE\tilde{y}}{\hbar \omega}\cos(\omega t)
    \bigg) \vartheta(\tilde{y},t),
\end{equation}
where $\vartheta(\tilde{y},t)$ is a function that satisfy the property
\begin{equation} \label{eq_a6}
    \bigg[
    \frac{m_e \omega_0^2}{2}\tilde{y}^2
    - {eE\tilde{y}}\sin(\omega t)
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}}
    - i \hbar \dv{t}
    \bigg]
    \vartheta(\tilde{y},t) = 0.
\end{equation}
If we turn off the dressing field ($E=0$), this equation leads to the Schrödinger equation with the simple harmonic oscillator Hamiltonian
\begin{equation} \label{eq_a7}
     i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    \frac{\hat{p}_{\tilde{y}}^2}{2m_e} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    \bigg]
    \vartheta(\tilde{y},t).
\end{equation}
Thus, we can identify $S(t) \equiv eE\sin(\omega t)$ term as an external force act on the harmonic oscillator, and we can solve this as a forced harmonic oscillator in $\tilde{y}$ axis
\begin{equation} \label{eq_a8}
  \begin{aligned}
    i \hbar \dv{\vartheta(\tilde{y},t)}{t} =
    \bigg[
    -
    \frac{\hbar^2}{2m_e}
    \pdv[2]{\tilde{y}} +
    \frac{1}{2}m_e \omega_0^2\tilde{y}^2
    - \tilde{y}S(t)]
    \bigg]
    \vartheta(\tilde{y},t).
  \end{aligned}
\end{equation}

This system is exactly solvable, and we can solve the equation using the methods explained by Husimi \cite{husimi53}. We introduce a time dependent shifted coordinate $ y' = \tilde{y} - \zeta(t)$ and perform the following unitary transformation
\begin{equation} \label{eq_a9}
    \vartheta(y',t) = \exp(\frac{im_e\dot{\zeta}y'}{\hbar})\varphi(y',t).
\end{equation}
This leads to
\begin{equation} \label{eq_a10}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   &=
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 y'^2 \\
        & +
        \Big[
            m_e\ddot{\zeta} + m_e\omega_0^2\zeta - S(t)
        \Big]y' \\
        &
        +
        \Big[
            - \frac{1}{2} m_e\dot{\zeta}^2 + \frac{1}{2}m_e\omega_0^2 \zeta^2 - \zeta S(t)
        \Big]
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Subsequenty, we can restrict $\zeta(t)$ function such that
\begin{equation} \label{eq_a11}
  m_e\ddot{\zeta} + m_e\omega_0^2\zeta = S(t),
\end{equation}
and that simply our previous expression as
\begin{equation} \label{eq_a12}
  \begin{aligned}
    i \hbar \pdv{\varphi(y',t)}{t}   =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}} &
        + \frac{1}{2} m_e \omega_0^2 {y'}^2 \\
        &
        - L(\zeta,\dot{\zeta},t)
    \bigg]\varphi(y',t).
  \end{aligned}
\end{equation}
Here
\begin{equation} \label{eq_a13}
  L(\zeta,\dot{\zeta},t) = \frac{1}{2} m_e\dot{\zeta}^2 - \frac{1}{2}m_e\omega_0^2 \zeta^2 + \zeta S(t),
\end{equation}
is the Lagrangian of a classical driven oscillator. To proceed further, another unitary transform can be introduced as follows
\begin{equation} \label{eq_a14}
    \varphi(y',t) = \exp(\frac{i}{\hbar}\int_0^{t}dt'L(\zeta,\dot{\zeta},t')) \chi(y',t),
\end{equation}
and subtitling Eq.~(\ref{eq_a14}) back in Eq.~(\ref{eq_a12}) yields
\begin{equation} \label{eq_a15}
    i \hbar \pdv{t} \chi(y',t)  =
    \bigg[
        -  \frac{\hbar^2}{2m_e}\pdv[2]{{y'}}
        + \frac{1}{2} m_e \omega_0^2 {y'}^2
    \bigg] \chi(y',t).
\end{equation}
This is the well-known Schrödinger equation of the quantum harmonic oscillator.
This allows us to identify the well known eigenfunctions \cite{griffiths18,shankar94}
\begin{equation} \label{eq_a16}
  \chi_n(y) =
   \frac{\sqrt{\kappa}}{\sqrt{2^{n}n!}}
  e^{-\kappa^2 y^2/2}
  \mathcal{H}_n \qty(\kappa y),
\end{equation}
with eigenvalues
\begin{equation} \label{eq_a17}
  \epsilon_n = \hbar \omega_0 \bigg(n + \frac{1}{2}\bigg)
  ~\text{for}~
  n \in \mathbb{Z}^{+}_0.
\end{equation}
Here, $\kappa = \sqrt{{m_e \omega_0}/{\hbar}}$, and $\mathcal{H}_n$ are the Hermite polynomials.
Thus, we can identify the solutions for Eq.~(\ref{eq_a8}) as
\begin{equation} \label{eq_a18}
  \begin{aligned}
    \vartheta_n(\tilde{y},t) = \chi_n(\tilde{y} - \zeta(t))
     \text{exp}\bigg(\frac{i}{\hbar}\bigg[&- \epsilon_nt +
    m_e\dot{\zeta(t)}\big[\tilde{y}-\zeta(t)\big] \\
     & + \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
Since $\chi_n(x)$ functions forms a complete set, any general solution $\vartheta_(\tilde{y},t)$ can be presented with the help of the solutions derived in Eq.~(\ref{eq_a18}).

Finally, we consider our scenario where we assumed that $S(t) = eE\sin(\omega t)$, and we derive the solution for Eq.~(\ref{eq_a11}) as
\begin{equation} \label{eq_a19}
  \zeta(t) = \frac{eE}{m_e(\omega_0^2 - \omega^2)}\sin(\omega t).
\end{equation}
Subtitling solutions in Eq.~(\ref{eq_a18}) back in Eq.~(\ref{eq_a5}), we obtain a set of wave functions with two different quantum number ($n$,$m$) that satisfy the time dependent Schrödinger equation Eq.~(\ref{eq_a4}) as follows
\begin{equation} \label{eq_a20}
  \begin{aligned}
    \psi_{n,m}&(x,y,t)  = \frac{1}{\sqrt{L_x}}
    \chi_n\left(y - y_0 - \zeta(t)\right)
    \text{exp}\bigg(
    \frac{i}{\hbar}\bigg[- \epsilon_nt \\
    &
    + p_x x + \frac{eE[y - y_0]}{\omega}\cos(\omega t)+
    m_e\dot{\zeta}(t)\big[y - y_0 -\zeta(t)\big]\\
    & +
    \int_0^{t}dt'L(\zeta,\dot{\zeta},t')\bigg]\bigg).
  \end{aligned}
\end{equation}
